sensi_an_rotations1. Start of sensitivity analysis for rotations.

### 2019-09-05 inst/documents/rotations_notes.Rmd
tidying

*13/7/18*

ltst <- list(d=c(9,6),s=7)

@@

Seems that with variable insecticides there are more runs where sequences are better (i.e. highly negative rot_minus_seq) ?

See :
df_res_all_rot1000-diffI-lowstart.rda

@@

~ added id to outputs in sensi_an_rotations to make things easier in future, e.g. to identify runs with particular behaviour.

~ also made more efficient by declaring size of results df at start of loop

@@

*13/11/2018*
preparing slides for IVCC talk next week

@@

23/11/18
#to output script as pdf for Ian to print
library(knitr)
stitch(script="R/run_rot.r")

@@

4/12/18
Met with Jim he offered to look at parallelising.

5/12/18
making scaled down version of sensi analysis for Jim

For rotations sent Jim a scaled down version of the rotations sensitivity analysis code. That just runs the sensitivity analysis and Jim will have a go at parallelising it.

6/12/18
Check why git changes are thinking that whole file has changed. How did I fix that for rnaturalearth ??

@@

6/2/19

before meeting with Jim to look at rotations code

previous error in raf_get() seems OK now

13/2/2019

looking at saving tested mortality levels for the different insecticides over time
(as a prelude to using it as a criteria for switching insecticides)

@@

14/2/2019

starting to get mortality recording working

currently looking at the df_mortali array from within a stop put inside run_rot()

@@

#20/2/2019

watched Ellies talk
~ she particularly talked about the benefit of combining complementary interventions in future (e.g. community larvel source management, ATSBs, etc.)
~ How these combine will depend on which part of the transmission cycle they target, e.g. outdoor biters
~ she showed quite nice cartoons of how untreated nets, treated nets and IRS can reduce tranmsission in different ways
~ made me think there may be potential to develop a clearer visualisation of the transmission cycle and how interventions can work, similar to stuff I did with Gerry
~ other interesting thing that Hilary asked about is how the different insecticides can modify both repellance and killing and how this may change due to resistance. Maybe similar to converstaions we had with Francis Rowland.
~ but I don't really have the inclination to move in the modelling direction but may be options to keep some interests going parallel with it.

@@

# 21/2/2019

Cool getting there with mortality checking :
Best to set logy to F to be able to see 90% mort

@@

# 26/2/2019

starting to get mortality switch working.

@@

1/3/19

Had idea to try to plot regio of parameter space where mortality less than 90%.
Not sure it is very useful, but did make a start.

@@

5/3/19
~ added mort_or_freq switch to rotresist1/ui.r
~ added threshold to UI

7/3/19

Using mortality switch for sequences, currently it switches back to other insecticides even when they are below threshold.

@@

@@

@@

fix :
Warning: Error in raf_get: object 'RAF' not found
run_rot() can create it but when I add breakpoints it disappears

@@

~ check on 1000 runs with lower startfreqs and differing insecticides 
~ is something weird going on favouring rotations more when insecticides differ ?
~ yes

@@

rotations paper :
~ develop flow of story
~ think about what questions managers will want answered

>>>>

*13/7/18*
ltst <- list(d=c(9,6),s=7)

@@

Seems that with variable insecticides there are more runs where sequences are better (i.e. highly negative rot_minus_seq) ?
See : df_res_all_rot1000-diffI-lowstart.rda

@@

~ added id to outputs in sensi_an_rotations to make things easier in future, e.g. to identify runs with particular behaviour.
~ also made more efficient by declaring size of results df at start of loop

@@

# 13/11/2018
preparing slides for IVCC talk next week

@@

# 23/11/18
to output script as pdf for Ian to print

library(knitr)
stitch(script="R/run_rot.r")

@@

# 5/12/18
For rotations sent Jim a scaled down version of the rotations sensitivity analysis code. That just runs the sensitivity analysis and Jim will have a go at parallelising it.

# 6/12/18
Check why git changes are thinking that whole file has changed. How did I fix that for rnaturalearth ??

@@

# 6/2/19
before meeting with Jim to look at rotations code
previous error in raf_get() seems OK now

# 13/2/2019
looking at saving tested mortality levels for the different insecticides over time
(as a prelude to using it as a criteria for switching insecticides)

@@

#14/2/2019
starting to get mortality recording working
currently looking at the df_mortali array from within a stop put inside run_rot()

@@

#20/2/2019
watched Ellies talk
~ she particularly talked about the benefit of combining complementary interventions in future (e.g. community larvel source management, ATSBs, etc.)
~ How these combine will depend on which part of the transmission cycle they target, e.g. outdoor biters
~ she showed quite nice cartoons of how untreated nets, treated nets and IRS can reduce tranmsission in different ways
~ made me think there may be potential to develop a clearer visualisation of the transmission cycle and how interventions can work, similar to stuff I did with Gerry
~ other interesting thing that Hilary asked about is how the different insecticides can modify both repellance and killing and how this may change due to resistance. Maybe similar to converstaions we had with Francis Rowland.
~ but I don't really have the inclination to move in the modelling direction but may be options to keep some interests going parallel with it.

@@

# 21/2/2019
Cool getting there with mortality checking :
Best to set logy to F to be able to see 90% mort

@@

# 26/2/2019
starting to get mortality switch working.

@@

#1/3/19
Had idea to try to plot regio of parameter space where mortality less than 90%.
Not sure it is very useful, but did make a start.

@@

#5/3/19
~ added mort_or_freq switch to rotresist1/ui.r
~ added threshold to UI

7/3/19
Using mortality switch for sequences, currently it switches back to other insecticides even when they are below threshold.

@@

# 4/9/19
However I change the run workflow I should try to keep it so that I can do the runs on multiple cores.

# 5/9/19

refactoring inputs
Currently the list linputs which has one row per run is created in sensi_an_rotations1.Rmd by hardcoded min-max limits

new inputs plan
Have a rotations function that accepts a csv file or defaults and uses that to create the linputs list, also it can save the csv. Closer to what resistance code did.

How to name the different files ? what are similar names in openMalaria ?

in_expt
in_runs

@@

~ investigate getting runs to name the output file with the date 
~ and create a similarly named metadata file that records run input params 
~ think about moving run control from a rmd to a .R script
~ think about being able to create named run inputs files (csv ?) that store the list of inputs (can be the same one that is saved as run metadata)

# RUNS FOR PAPER September 2019
# A identical insecticides, seq vs rot, resistance frequency switch, A1 no costs no dispersal, A2 costs no dispersal, A3 dispersal no costs, A4 costs & dispersal. Sensitivity analysis of inputs.
# B different insecticides, as above, no sensitivity analysis.
# C identical insecticides, mortality switch, reduced input range so mortality starts above 90%
# D different insecticides, mortality switch

Runs are combinations of :
Strategy (2)       : sequence, rotation
Insecticides (2)   : same, different
Switch (2)         : resistance frequency, mortality
Scenarios (4)      : no costs no dispersal, costs no dispersal, dispersal no costs, costs & dispersal
Replicates (10000) :

So number of runs 2*2*2*4*10000 = 320000

@@

I think this is fixed now :
Warning: Error in raf_get: object 'RAF' not found
run_rot() can create it but when I add breakpoints it disappears

@@

@@

rotations paper :
~ think about what questions managers will want answered

### 2019-09-05 inst/documents/sensi_an_rotations1.Rmd
tidying

@@

    # rbind this scenario inputs & results onto previous
    # not a good speed or memory way of doing ... but a start
    #df_res_all <- rbind(df_res_all, df_in_out)

@@

@@

  #converting multiple insecticide inputs back from strings
  #have to ignore the ones that aren't strings
  #linputs2 <- lapply(linputs, function(x) as.numeric(unlist(strsplit(as.character(x),split=", "))))

@@

  #TESTING changing min_rwr_interval from 5
  #if min_rwr_interval is set to 0 you get frequent switch backs to other insecticides 
  #for 1 generation
  #but when it's set to 5it pushes frequences above the resistance freq threshold
  linputs$min_rwr_interval <- 5
  #min_gens_switch_back has to be 0 to allow one insecticide to continue when all others dead
  linputs$min_gens_switch_back = 0

@@

>>>>

    #beware min_rwr_interval, it's to stop repeated small rotations
    linputs$min_rwr_interval <- 5
    linputs$min_gens_switch_back <- 1
    linputs$no_r_below_start <- FALSE #BEWARE this has been set to TRUE in all earlier runs
    linputs$no_r_below_mut <- FALSE #BEWARE trying out new mutation-selection balance option
    #set plot to F if using grid.arrange as in phaps-rotations-better.Rmd
    linputs$plot <-     FALSE

@@

@@

    #save partial outputs just in case doesn't make to end
    if (i%%1000 == 0)
    {
      #df_res_all$rot_minus_seq <- df_res_all$gens_rot - df_res_all$gens_seq

@@

  #converting multiple insecticide inputs back from strings
  #have to ignore the ones that aren't strings

@@

  #TESTING changing min_rwr_interval from 5
  #if min_rwr_interval is set to 0 you get frequent switch backs to other insecticides for 1 generation
  #but when it's set to 5 it pushes frequences above the resistance freq threshold
  linputs$min_rwr_interval <- 5
  #min_gens_switch_back has to be 0 to allow one insecticide to continue when all others dead
  linputs$min_gens_switch_back = 0

@@

  # now run as sequence
  linputs$rot_interval <- 0
  dfres <- do.call(run_rot, linputs)
